\documentclass{article}
\usepackage{longtable}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{margin=1in}
\begin{document}

\renewcommand{\arraystretch}{1.2}
\setlength{\tabcolsep}{6pt}

\begin{longtable}{|p{3.5cm}|p{5cm}|p{3.5cm}|p{2cm}|}
\hline
\textbf{Benchmark} & \textbf{Description / Tasks} & \textbf{Metrics} & \textbf{Citation / Resource} \\
\hline
\endfirsthead
\hline
\textbf{Benchmark} & \textbf{Description / Tasks} & \textbf{Metrics} & \textbf{Citation / Resource} \\
\hline
\endhead

\hline
\endfoot

BaisBench & 
Cell type annotation and scientific discovery in single-cell omics studies. & 
Accuracy & 
\cite{@misc{luo2025benchmarkingaiscientistsomics}} \newline \url{https://arxiv.org/abs/2505.08341} \\
\hline

MOLGEN & 
Generating novel molecules with desired properties. & 
Diversity, Validity, Novelty, Property scores & 
\url{https://github.com/zjunlp/MolGen} \\
\hline

OGB - Biology & 
Graph ML on biological networks (PPI, DTI). Tasks: Node classification, link prediction. & 
Accuracy, AUC & 
\cite{@misc{hu2021opengraphbenchmarkdatasets}} \newline \url{https://ogb.stanford.edu/docs/home/} \\
\hline

Materials Project & 
Predict material properties like bandgaps, formation energies. & 
MAE, R\textsuperscript{2} & 
\url{https://materialsproject.org/} \\
\hline

Open Catalyst Project (OCP) & 
Predict adsorption energies and reaction outcomes for catalysts. & 
MAE (energies, forces) & 
\url{https://opencatalystproject.org/} \\
\hline

JARVIS-Leaderboard & 
Material property prediction, image classification in STEM, force field prediction. & 
Task-specific metrics (e.g., MAE) & 
\url{https://pages.nist.gov/jarvis_leaderboard/} \\
\hline

Quantum Computing Benchmarks & 
Quantum state preparation, circuit optimization, error correction. & 
Fidelity, Success probability & 
\url{https://github.com/XanaduAI/qml-benchmarks}, \newline \url{https://pennylane.ai/datasets/collection/qml-benchmarks} \\
\hline

CFDBench & 
AI for computational fluid dynamics (CFD). Solve Navier-Stokes, predict flow. & 
L2 error & 
\cite{@misc{luo2024cfdbenchlargescalebenchmarkmachine}} \newline \url{https://arxiv.org/abs/2310.05963} \\
\hline

SatImgNet & 
Satellite image analysis: object detection, segmentation, change detection. & 
mAP, IoU, Accuracy & 
(No paper or official link) \\
\hline

Climate Model Benchmarks & 
Forecasting temperature, precipitation, extreme weather events. & 
RMSE, Bias & 
\cite{@misc{nguyen2023climatelearnbenchmarkingmachinelearning}} \newline \url{https://arxiv.org/abs/2307.01909} \\
\hline

BIG-Bench & 
General reasoning and knowledge benchmark across many domains. & 
Accuracy, Task-specific & 
\cite{@article{srivastava2023beyond}} \newline \url{https://github.com/google/BIG-bench} \\
\hline

CommonSenseQA & 
Multiple-choice QA requiring commonsense reasoning. & 
Accuracy & 
\cite{@misc{alontalmor2019commonsenseqa}} \newline \url{https://paperswithcode.com/paper/commonsenseqa-a-question-answering-challenge} \\
\hline

Winogrande & 
Disambiguating context-rich sentences using commonsense. & 
AUC & 
\url{https://leaderboard.allenai.org/winogrande/submissions/public} \\
\hline

\end{longtable}

\end{document}
